---
title: "Tidy Tuesday: "
author: "Andrew Stewart"
date: !r Sys.Date()
output:
  html_document:
    theme: paper
    highlight: kate
editor_options:
  chunk_output_type: console
params:
  week: !r tidytuesdayR::last_tuesday()
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, fig.showtext = T, fig.retina = 1)

# Packages
library(tidytuesdayR)
library(tidyverse)
library(janitor)
library(here)
library(ggplot2)
library(patchwork)

theme_set(theme_minimal())

# First update the tidyduesdayR master file
tidytuesdayR:::tt_update_master_file(force=TRUE)
```

# Create workspace

```{r}
fs::dir_create(here(params$week))
```


# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load(params$week)

```

# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

```{r Skim}

tt %>% 
  map(skimr::skim)

```


# Explore

Generate exploratory data report using DataExplorer

```{r Explore}
create_report(tt$plants, 
              output_file = "plants.html", 
              output_dir = here::here(params$week))
create_report(tt$threats, 
              output_file = "threats.html", 
              output_dir = here::here(params$week))
create_report(tt$actions, 
              output_file = "actions.html", 
              output_dir = here::here(params$week))

```


# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

df <- tt$plants

```

# Visualize

Using your processed dataset, create your unique visualization.


```{r}

# Trying out the waffle plot theme from https://github.com/kellycotton/TidyTuesdays/blob/master/code/plants.R

library(tidyverse)
library(waffle)
library(hrbrthemes)
library(futurevisions)
library(patchwork)

plants <- tidytuesdayR::tt_load(2020, week = 34)$plants

plants <- plants %>%
  mutate(across(where(is.character), as.factor))
plants$year_last_seen <- factor(plants$year_last_seen, 
                                levels = c("Before 1900", "1900-1919", "1920-1939", "1940-1959", "1960-1979", "1980-1999", "2000-2020"))

plants %>%
  count(continent) %>%
  ggplot(aes(fill = continent, values = n)) +
  geom_waffle(n_rows = 25, size = 0.25, colour = "black", flip = TRUE) +
  coord_equal() +
  scale_fill_manual(values = futurevisions("grand_tour"), name = element_blank(), limits = rev(levels(plants$continent))) +
  theme_ft_rc(grid="") +
  theme_enhance_waffle() + 
  theme(
    plot.subtitle = element_text(hjust = .5),     
    plot.margin = unit(c(0,0,.5,0), "cm"),
    legend.key.width = unit(.4,"cm"), 
    legend.key.height = unit(.4,"cm"),
    legend.text = element_text(size = 9)
  ) + labs(subtitle = "Where?")


```


# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  path = here::here(params$week),
  filename = "tt.png",
  device = "png")

```

# Session info

```{r session}
Sys.time()
git2r::repository()
sessionInfo()
```
