---
title: "Avatar"
author: "Andrew Stewart"
date: !r Sys.Date()
output:
  html_document:
    theme: paper
    highlight: kate
editor_options:
  chunk_output_type: console
params:
  week: !r tidytuesdayR::last_tuesday()
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, fig.showtext = T, fig.retina = 1)

# Packages
library(tidytuesdayR)
library(tidyverse)
library(janitor)
library(here)
library(ggplot2)
library(patchwork)

theme_set(theme_minimal())

# First update the tidyduesdayR master file
tidytuesdayR:::tt_update_master_file(force=TRUE)
```


# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load(params$week)

```

# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

```{r Skim}

tt %>% 
  map(skimr::skim)

```


# Explore

Generate exploratory data report using DataExplorer

```{r Explore}
library(DataExplorer)
create_report(tt$avatar, 
              output_file = "avatar.html", 
              output_dir = here::here(params$week))

```


# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

df <- tt

```

# Visualize

Using your processed dataset, create your unique visualization.

```{r}

df %>%
  ggplot()

```


# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  path = here::here(params$week),
  filename = "tt.png",
  device = "png")

```

# Session info

```{r session}
Sys.time()
git2r::repository()
sessionInfo()
```
