---
title: "Tidy Tuesday: "
author: "Andrew Stewart"
date: !r Sys.Date()
output:
  html_document:
    theme: paper
    highlight: kate
editor_options:
  chunk_output_type: console
params:
  week: '2020-09-08'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, fig.showtext = T, fig.retina = 1)

# Packages
library(tidytuesdayR)
library(tidyverse)
library(janitor)
library(here)
library(ggplot2)
library(patchwork)
library(waffle)

theme_set(theme_minimal())

# First update the tidyduesdayR master file
tidytuesdayR:::tt_update_master_file(force=TRUE)
```

# Create workspace

```{r}
fs::dir_create(here(params$week))
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load(params$week)

```

# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

```{r Skim}

tt %>% 
  map(skimr::skim)

```


# Explore

Generate exploratory data report using DataExplorer

```{r Explore}

create_report(data, 
              output_file = "report.html", 
              output_dir = here::here(params$week))

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
main_friends <- tt$friends %>% 
  tabyl(speaker) %>% 
  arrange(desc(n)) %>% 
  head(6) %>% 
  pull(speaker)

# df <- tt
df <- tt$friends %>%
  count(season, speaker) %>%
  filter(speaker %in% main_friends)
```



# Visualize

Using your processed dataset, create your unique visualization.

```{r}

ggplot(df, aes(fill = speaker, values = n)) +
  geom_waffle(color = "white", size = .25, n_rows = 10, flip = TRUE) +
  facet_wrap(~season, nrow = 1, strip.position = "bottom") +
  scale_x_discrete() + 
  scale_y_continuous(labels = function(x) x * 10, # make this multiplyer the same as n_rows
                     expand = c(0,0)) +
  ggthemes::scale_fill_tableau(name=NULL) +
  coord_equal() +
  labs(
    title = "Faceted Waffle Bar Chart",
    subtitle = "{dplyr} storms data",
    x = "Year",
    y = "Count"
  ) +
  theme_minimal(base_family = "Roboto Condensed") +
  theme(panel.grid = element_blank(), axis.ticks.y = element_line()) +
  guides(fill = guide_legend(reverse = TRUE))

```


# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  path = here::here(params$week),
  filename = "tt.png",
  device = "png")

```

# Session info

```{r session}
Sys.time()
git2r::repository()
sessionInfo()
```
