---
title: "TidyTemplate"
date: 2020-08-04
output:
  html_document:
    theme: paper
    highlight: kate
editor_options:
  chunk_output_type: console
params:
  week: !r tidytuesdayR::last_tuesday()
  foo: !r rmarkdown::metadata$title
---

```{r}
rmarkdown::metadata$title
```


# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.showtext = T, fig.retina = 1)
library(janitor)
library(tidyverse)
library(tidytuesdayR)
library(ggplot2)
library(cowplot)
require(maps)
require(viridis)
library(pdftools)

# theme_set(theme_minimal())

theme_set(
  theme_void()
  )
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2020-08-04")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```

# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse, eval=FALSE, include=FALSE}

tt %>% 
  map(glimpse)

```

```{r eval=FALSE, include=FALSE}
for(i in names(tt))
  DataExplorer::create_report(tt[[i]],
                output_file = glue::glue("{i}.html"),
                output_dir = here::here(params$week))

DataExplorer::create_report(tt$energy_types,
                output_file = glue::glue("energy_types.html"),
                output_dir = here::here(params$week))

```



# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

df <- tt$energy_types %>%
  pivot_longer(
    cols = c('2016','2017','2018'),
    names_to = 'year',
    values_to = 'energy'
  )
df %>%
  group_by(country, country_name, type, year) %>%
  summarize(energy = sum(energy)) %>%
  arrange(country)
```

```{r}
tt$country_totals %>%
  pivot_longer(
    cols = c('2016','2017','2018'),
    names_to = 'year',
    values_to = 'energy'
  ) %>%
arrange(country)
```



# Visualize

Using your processed dataset, create your unique visualization.

```{r}
# Some EU Contries
some.eu.countries <- c(
  "Portugal", "Spain", "France", "Switzerland", "Germany",
  "Austria", "Belgium", "UK", "Netherlands",
  "Denmark", "Poland", "Italy", 
  "Croatia", "Slovenia", "Hungary", "Slovakia",
  "Czech republic", "Finland","Sweden"
)
# Retrievethe map data
some.eu.maps <- map_data("world", region = some.eu.countries)

# Compute the centroid as the mean longitude and lattitude
# Used as label coordinate for country's names
region.lab.data <- some.eu.maps %>%
  group_by(region) %>%
  summarise(long = mean(long), lat = mean(lat))

ggplot(some.eu.maps, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = region))+
  geom_text(aes(label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
  scale_fill_viridis_d()+
  theme_void()+
  theme(legend.position = "none")
```


```{r Visualize}
## Following examples from https://www.datanovia.com/en/blog/how-to-create-a-map-using-ggplot2/

# Some EU Contries
some.eu.countries <- c(
  "Portugal", "Spain", "France", "Switzerland", "Germany",
  "Austria", "Belgium", "UK", "Netherlands",
  "Denmark", "Poland", "Italy", 
  "Croatia", "Slovenia", "Hungary", "Slovakia",
  "Czech republic"
)
# Retrievethe map data
regions <- df %>% drop_na(country_name) %>% pull(country_name) %>% unique()
some.eu.maps <- map_data("world", region = regions)

# Compute the centroid as the mean longitude and lattitude
# Used as label coordinate for country's names
region.lab.data <- some.eu.maps %>%
  group_by(region) %>%
  summarise(long = mean(long), lat = mean(lat))

df %>%
  filter(year == 2016) %>%
  rename(region = country_name) %>%
  left_join(some.eu.maps, by = "region") %>%
  ggplot(aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = energy))+
  # geom_text(aes(label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
  scale_fill_viridis_c(option = "d")+
  theme_void()+
  theme(legend.position = "none")  -> p1

df %>%
  filter(year == 2017) %>%
  rename(region = country_name) %>%
  left_join(some.eu.maps, by = "region") %>%
  ggplot(aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = energy))+
  # geom_text(aes(label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
  scale_fill_viridis_c(option = "d")+
  theme_void()+
  theme(legend.position = "none")  -> p2

df %>%
  filter(year == 2018) %>%
  rename(region = country_name) %>%
  left_join(some.eu.maps, by = "region") %>%
  ggplot(aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = energy))+
  # geom_text(aes(label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
  scale_fill_viridis_c(option = "d")+
  theme_void()+
  theme(legend.position = "none")  -> p3

df %>%
  ggplot(aes(fill=type, x=year, y=energy)) +
  geom_boxplot() +
  scale_y_log10() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) -> p4
```

```{r}
library(patchwork)
# p1 <- ggplot(cars, aes(x=speed)) + geom_histogram()
# p2 <- ggplot(cars, aes(x=speed)) + geom_histogram()
# p3 <- ggplot(cars, aes(x=speed)) + geom_histogram()
patch <- ((p1 + p2 + p3) / p4) + # Defining pathwork layout
  
  plot_layout(guides = 'collect') + # Collecting guides on the right side
  
  # Annotations
  plot_annotation(
    title = "European Energy",
    caption = "@andrewcstewart on #TidyTuesday. Data from Eurostat.") &
  
  # Small theme tweaks
  theme(plot.title = element_text(size = 30, hjust=0.5), # Centering title and changing size
        panel.grid = element_line(color = 'white'), # Hiding gridlines
        text = element_text(family = 'Avenir Book')) # Changing font
 
patch
```


```{r}
# from https://cran.r-project.org/web/packages/tricolore/vignettes/choropleth_maps_with_tricolore.html
library(tricolore)

# color-code the data set and generate a color-key
tric <- Tricolore(euro_example, p1 = 'ed_0to2', p2 = 'ed_3to4', p3 = 'ed_5to8')

# add the vector of colors to the `euro_example` data
euro_example$rgb <- tric$rgb

library(ggplot2)

plot_educ <-
  # using sf dataframe `euro_example`...
  ggplot(euro_example) +
  # ...draw a polygon for each region...
  geom_sf(aes(fill = rgb, geometry = geometry), size = 0.1) +
  # ...and color each region according to the color code in the variable `rgb`
  scale_fill_identity()

plot_educ 
```

```{r}
euro_example %>%
  mutate(country = str_sub(id, 1, 2)) %>%
  left_join(df, by = "country") %>%
  drop_na(type, year) %>%
  ggplot() +
  geom_sf(aes(fill = energy, geometry = geometry), size = 0.1) +
  scale_fill_viridis_c(option = "C", 
                       # guide = guide_legend(legend.key.size = unit(1.5, "cm"))
                      ) +
  theme(legend.position='bottom') +
  facet_grid(year ~ type, switch = "y") -> p1

  # ...and color each region according to the color code in the variable `rgb`
  # scale_fill_identity()
```

```{r}

patch <- ((p1)) + # Defining pathwork layout
  
  plot_layout(guides = 'collect') + # Collecting guides on the right side
  
  # Annotations
  plot_annotation(
    title = "European energy generation",
    caption = "@andrewcstewart on #TidyTuesday. Data from Eurostat.") &
  
  # Small theme tweaks
  theme(plot.title = element_text(size = 30, hjust=0.5), # Centering title and changing size
        panel.grid = element_line(color = 'white'), # Hiding gridlines
        legend.position='bottom',
        text = element_text(family = 'Avenir Book')) # Changing font
 
patch
```


# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
# ggsave(
#   path = here::here(params$week),
#   filename = "final.png",
#   device = "png")

ggsave(
  path = here::here(params$week),
  filename = "final.png",
  width = 16, 
  height = 7, 
  device = "png")
```

```{r}
# pdf_convert(pdf = here::here(params$week, "final.pdf"),
            # format = "png", dpi = 500)

```

# Session info

```{r session}
Sys.time()
git2r::repository()
sessionInfo()
```
