---
title: "Tidy Tuesday: "
author: "Andrew Stewart"
date: !r Sys.Date()
output:
  html_document:
    theme: paper
    highlight: kate
editor_options:
  chunk_output_type: console
params:
  week: "2020-08-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, fig.showtext = T, fig.retina = 1)

# Packages
library(tidytuesdayR)
library(tidyverse)
library(janitor)
library(here)
library(ggplot2)
library(patchwork)
library(ggpubr)

# theme_set(theme_minimal())

# First update the tidyduesdayR master file
tidytuesdayR:::tt_update_master_file(force=TRUE)
```

# Create workspace

```{r}
fs::dir_create(here(params$week))
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load(params$week)

```

# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

```{r Skim}

tt %>% 
  map(skimr::skim)

```


# Explore

Generate exploratory data report using DataExplorer

```{r Explore}

DataExplorer::create_report(tt$chopped, 
              output_file = "chopped.html", 
              output_dir = here::here(params$week))

```


# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

df <- tt$chopped %>%
  pivot_longer(cols = starts_with("judge"),
               values_to = "judge") %>%
  select(judge, everything())
```

# Visualize

Using your processed dataset, create your unique visualization.

## Idea 1

Let's turn the tables and evaluate the judges based on their ratings.

For this plot I want to try out a few things:

- `ggpubr`'s dot charts.
- 

```{r}
ggthemr('fresh')
p1 <- df %>%
  group_by(judge) %>%
  summarise(avg_rating = mean(episode_rating, na.rm = TRUE),
            n = n()) %>%
  ungroup() %>%
  filter(n > 3) %>%
  mutate(num_episodes = cut_interval(n, n = 3)) %>%
  ggdotchart(x = "judge", y = "avg_rating",
             color = "num_episodes",                       # Color by groups
             palette = c("#00AFBB", "#E7B800", "#FC4E07"), # Custom color palette
             sorting = "descending",                       # Sort value in descending order
             # add = "segments",
             rotate = TRUE,                                # Rotate vertically
             dot.size = 2,                                 # Large dot size
             y.text.col = TRUE,                            # Color y text by groups
             title = "imdb rating",
             ylab = FALSE,
             xlab = FALSE,
             ggtheme = theme_pomological("Homemade Apple", 12)                       # ggplot2 theme
             ) +
  xlab("Average IMDB Rating")
  # theme_cleveland()
p1
```


```{r}

```


```{r}
# ggthemr('fresh')
p1 + plot_annotation(
    title = "Chopped!",
    subtitle = "Let's turn the tables and evaluate the judges!",
    caption = "Created by @andrewcstewart, Data from Kaggle, #TidyTuesday",
    theme = theme_pomological("Homemade Apple", 16)) 
```


# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  path = here::here(params$week),
  filename = "chopped.png",
  device = "png")

```

# Session info

```{r session}
Sys.time()
git2r::repository()
sessionInfo()
```
